---
title: Readme for EpiScore.R function
author: X Shen  
date: "\n`r format(Sys.time(), '%d %B, %Y')`"
output: github_document
---

## Summary

-   AD use data preparation: prep.AD_phenotype.Rmd

-   Proteomic data and covariates preparation: prep.prot_covs.Rmd

```{r libraries, messages=FALSE, echo=F}
library(readr)           # Data loading/writing
library(dplyr)           # Data management
library(tidyr)           # Data management
library(stringr)         # Text processing
library(lubridate)       # Text processing
library(pbapply)         # Process control
library(knitr)           # Report generation
```

## Mandatory Input Data

### Methylation data

-   Input format: folder; Flag: --methFolder

-   Description: DNAm data should be stored in .rds format. Columns are participants and rows are CpG sites.

-   Example

```{r,echo=FALSE}
D_METH = matrix(runif(100),nrow=10) %>% 
  data.frame %>% 
  mutate(ID=paste0('subj',1:10)) %>% 
  select(ID,everything())
colnames(D_METH)[2:ncol(D_METH)] = paste0('cg',sample(10000000:99999999,size=10))
# use knirt to print D_METH
kable(D_METH)
```

### Sumstats from training model

-   Input format: .tsv file; Flag: --lassoCoef

-   Description: A file with two columns, the first one for subject IDs and the other for weights. The first row should be the header.

-   Example

```{r,echo=FALSE}
D_PHENO = data.frame(ID=sample(1:100,10) %>% paste0('pheno_SubjID_',.),pheno=runif(10))
kable(D_PHENO)
```


## Optional Inputs

### Subject IDs

-   Input format: .tsv file

-   Description: A file with one column of DNAm IDs for individuals to include in the analysis.

-   Example

```{r,echo=FALSE}
D_IDs = data.frame(ID_meth=colnames(D_METH))
kable(D_IDs)
```


------------------------------------------------------------------------

## Example Script:

Call the function from terminal:

```{bash,eval=F}
Rscript EpiScore.R --methFolder data/GS_DNAm \
--lassoCoef result/LASSO_weights_MDD \
--out result/episcore_mdd
```

```{bash,eval=F}
Rscript EpiScore.R --methFolder mval_test \
--lassoCoef LASSO_weights_MDD \
--out episcore_mdd
```
