---
title: Readme for LASSO_DNAm.R function
author: X Shen  
date: "\n`r format(Sys.time(), '%d %B, %Y')`"
output: github_document
---

## Summary

-   AD use data preparation: prep.AD_phenotype.Rmd

-   Proteomic data and covariates preparation: prep.prot_covs.Rmd

```{r libraries, messages=FALSE}
library(readr)           # Data loading/writing
library(dplyr)           # Data management
library(tidyr)           # Data management
library(stringr)         # Text processing
library(lubridate)       # Text processing
library(pbapply)         # Process control
library(knitr)           # Report generation
```

## Mandatory Input Data

### Methylation data

-   Input format: folder; Flag: --methFolder

-   Description: DNAm data should be stored in .rds format. Columns are participants and rows are CpG sites.

-   Example

```{r,echo=FALSE}
D_METH = data.frame(Subj1=runif(10),Subj2=runif(10),Subj3=runif(10),Subj4=runif(10),Subj5=runif(10))
rownames(D_METH) = paste0('cg',sample(10000000:99999999,size=10))
# use knirt to print D_METH
kable(D_METH)
```

### Phenotype data

-   Input format: .tsv file; Flag: --phenoFile

-   Description: A file with two columns, the first one for subject IDs and the other for phenotype values. The first row should be the header.

-   Example

```{r,echo=FALSE}
D_PHENO = data.frame(ID=sample(1:100,10) %>% paste0('pheno_SubjID_',.),pheno=runif(10))
kable(D_PHENO)
```

### Other inputs

-   Is the phenotype binary or continuous?

    -   Flag: --phenoBinary

    -   Options: yes/no (Default = 'no')

-   Output file

    -   Flag: --outputFile

## Optional Inputs

### Subject IDs

-   Input format: .tsv file

-   Description: A file with two columns, the first one for DNAm IDs and the other for phenotype IDs. The first row should be the header.

-   Example

```{r,echo=FALSE}
D_IDs = data.frame(ID_meth=rownames(D_METH),ID_pheno=sample(1:100,10) %>% paste0('pheno_SubjID_',.))
kable(D_IDs)
```

### CpGs to include

-   Input format: .tsv file

-   Description: A file with one column for CpG sites. The first row should be the header.

-   Example

```{r,echo=FALSE}
D_CPGs = data.frame(cpg=rownames(D_METH)[1:5])
kable(D_CPGs)
```

### Other optional input

-   Name of phenotype

    -   Flag: –phenoName

------------------------------------------------------------------------

## Example Script:

Call the function from terminal:

```{bash,eval=F}
Rscript LASSO_DNAm.R --methFolder data/GS_DNAm \
--phenoFile data/MDD.tsv \
--phenoBinary yes \
--phenoName MDD \
--subID data/DNAm_pheno_linkage.tsv \
--outputFile result/LASSO_weights_MDD
```
